Bootstrap Confidence Intervals for Sharp Regression Discontinuity Designs with the Uniform Kernel

### 2016-02-29 main_paper.tex
Make small changes to 'background' section of the paper

In most cases the population parameter of interest is the Average Treatment
Effect (ATE) at the cutoff, which we will denote $\tau$. This parameter is the
difference in expected potential outcomes given $X_i = 0$; formally,
\begin{equation*}
  \tau=\E(Y(1)-Y(0) \mid X=0).
\end{equation*}
\cite{HTV2001} show that the effect $\tau$ is identified under continuity and
smoothness conditions on the joint distribution of $X_i$, $Y_i(0)$, and $Y_i(1)$
around the cutoff $X_i = 0$. When these conditions hold, which are made precise
in Assumption~\ref{A1}, $\tau$ is equal to
\begin{equation*}
  \tau = \lim_{x \to 0+} \mu(x) - \lim_{x \to 0-}(x)
\end{equation*}
where
\begin{equation*}
  \mu(x)= \E(Y_{i} \mid X_{i}=x).
\end{equation*}
For convenience, also define
\begin{equation*}
  \mu^{(\eta)}(x)=\frac{d^{\eta}\mu(x)}{dx^{\eta}}
\end{equation*}
and let
\begin{align*}
  \mu_{+}(x)
  &= \E( Y_{i}(1) \mid X_{i}=x )
  &\mu_{-}(x)
  &= \E( Y_{i}(0) \mid X_{i}=x ) \\
  \sigma^{2}_{+}(x) &= \V( Y_{i}(1) \mid X_{i}=x )
  &\sigma^{2}_{-}(x)&=\V( Y_{i}(0) \mid X_{i}=x ) \\
\intertext{and}
  \mu^{(\eta)}_{+}
  &= \lim_{x \rightarrow 0^{+}}\mu^{(\eta)}(x),
  &\mu^{(\eta)}_{-}
  &= \lim_{x \rightarrow 0^{-}}\mu^{(\eta)}(x),
\end{align*}
where the symbol $\V(\cdot)$ represents the variance.  The effect $\tau$ is
nonparametrically identified because both $\mu_-$ and $\mu_+$ can be estimated
consistently under the conditions spelled out in Assumption~\ref{A1}.

@@

These conditions are standard in the RD literature. (See, in particular,
\citealp{HTV2001}, \citealp{Porter03}, and CCT). The third part of the
assumption is especially important for the characterization of the leading bias
term drives CCT's bias correction and our bootstrap procedure.

Since the conditions for identification only need to hold in a neighborhood
around the cutoff, $\mu_+$ and $\mu_-$ can be estimated by extrapolating from a
local polynomial regression.  We will focus here on local linear
regression.\footnote{%
  See \cite{HTV2001}, \cite{Porter03} or \cite{FanGijbels92} for discussions of
  the properties of local polynomial regressions for boundary problems. The
  bootstrap algorithm proposed in this paper can be extended to accommodate
  higher order polynomials discontinuities in the derivatives of the conditional
  expectation, like ``Kink RD'' design \citep{card2009b}. We focus on the linear
  case for ease in exposition.} %
For this model, if $h$ represents a bandwidth parameter, the estimator of
$\tau$, $\hat\tau(h)$, is
\begin{equation*}
  \hat{\tau}(h) = \hat {\mu}_{+}(h) -\hat{\mu}_{-}(h)
\end{equation*}
with
\begin{align*}
  (\hat {\mu}_{+}(h),\ \hat {\mu}^{(1)}_{+}(h))'
  &= \argmin_{\mu, \beta} \sum_{i=1}^{n}
  \1\{h > X_{i} \geq 0\} (Y_{i} - \mu - X_{i} \beta)^{2}
\intertext{and}
  (\hat {\mu}_{-}(h),\hat {\mu}^{(1)}_{-}(h))'
  &= \argmin_{\mu,\beta} \sum_{i=1}^{n}
  \1\{0 > X_{i} > -h \} (Y_{i} - \mu - X_{i} \beta)^{2}.
\end{align*}
Conventional (naive) confidence intervals can be calculated by using an
asymptotic approximation for $\hat\tau(h)$. In particular, if
\begin{gather}
  \label{eq:1}
  T(h) =\frac{\hat{\tau}(h)-\tau}{\sqrt{V(h)}} \to^d N(0,1),
  \intertext{with}
  \notag
  V(h) \big/ \V(\hat\tau(h) \mid X_{1},\dots,X_{n}) \to^p 1
\end{gather}
then valid confidence intervals can be constructed through the usual method of
inverting the $t$-test. This procedure gives the widely-used interval estimator
\begin{equation*}
  \hat{\tau}(h) \pm q_{1-\alpha/2} V(h)^{1/2}
\end{equation*}
where $q_{1 - \alpha/2}$ is the $1 - \alpha/2$ quantile of the standard normal
distribution.

The statistical properties of these estimators, however, clearly depend on the
bandwidth parameter $h$, and bandwidths that have desirable properties for point
estimation may not have desirable properties for hypothesis testing or interval
estimation. In particular, for~\eqref{eq:1} to hold, $h$ must satisfy
$n h \to \infty$ and $n h^5 \to 0$. (\citealp{HTV2001}; \citealp{Porter03})
Otherwise, the finite-sample bias of $\hat\tau(h)$ does not converge in
probability to zero quickly enough and it contributes non-negligibly to the
asymptotic distribution~\eqref{eq:1}. This result holds even though
$\hat\tau(h)$ can be consistent under those conditions.  These bandwidth issues
are relevant in practice because many widely-used bandwidth selection
procedures, most notably the AMSE-optimal bandwidth and cross-validation
bandwidth \citep{IK} do not satisfy this condition.

CCT solve this problem by deriving the analytical form of the first-order bias
and explicitly recentering $\hat\tau(h)$. Under weaker assumptions on the
asymptotic behavior of the bandwidth, which we will specify in
Assumption~\ref{A2}, CCT show that the approximate bias of $\hat\tau(h)$ has the
form
\begin{equation*}
  \E(\hat{\tau}(h) \mid \chi_{n}) - \tau =
  h^{2}\Big[ \tfrac{\mu_{+}^{(2)}}{2}\Bf_{+}(h)
  - \tfrac{\mu_{-}^{(2)}}{2}\Bf_{-}(h) \Big]
  (1+o_{p}(1))
\end{equation*}
where $\Bf_{+}(h)$ and $\Bf_{-}(h)$ are observed quantities that depend on the
kernel, bandwidth, and running variables $X_1,\dots,X_n$; formal definitions of
these terms are given in the Mathematical Appendix as Equations~\eqref{eq:5}
and~\eqref{eq:6}. The plug-in bias-corrected estimator then requires estimates
for the second derivatives of the conditional mean from above and below the
cutoff, $\mu_{+}^{(2)}$ and $\mu_{-}^{(2)}$, and CCT show that these derivatives
can be estimated by fitting a second order local polynomial, i.e. one order
higher than the polynomial used to obtain $\hat{\tau}$, using a (potentially)
different pilot bandwidth $b$. Their procedure gives the bias-corrected
estimator
\begin{gather*}
  \hat{\tau}'(h, b) = \hat{\tau}(h) - h^{2}
  \Big[\tfrac{\hat{\mu}_{+}^{(2)}(b)}{2} \Bf_{+}(h)
  - \tfrac{\hat{\mu}_{-}^{(2)}(b)}{2}\Bf_{-}(h) \Big]
\end{gather*}
The variance introduced by the bias-correction term does not vanish, so the
naive confidence interval needs not only to be re-centered to correct the bias,
but also rescaled to allow for the additional variability introduced by the bias
correction, resulting in the following asymptotic approximation:
\begin{equation*}
  T'(h, b) = \frac{\hat{\tau}'(h, b) - \tau}{V'(h, b)^{1/2}}
  \to^d N(0,1)
\end{equation*}
with $V'(h, b) = V(h) + C(h, b)$ and $C(h, b)$ an additional variance component
generated by the bias-correction term. This new approximation can be used
instead of~\eqref{eq:1} to construct ``bandwidth robust'' confidence intervals,
and CCT provide simulation evidence that their intervals perform well in finite
samples.

>>>>

In most cases the population parameter of interest is the Average Treatment
Effect (ATE) at the cutoff, which we will denote $\tau$. This parameter is the
difference in expected potential outcomes given $X_i = 0$; formally,
\begin{equation*}
  \tau=\E(Y(1)-Y(0) \mid X=0).
\end{equation*}
\cite{HTV2001} show that the effect $\tau$ is identified under continuity and
smoothness conditions on the joint distribution of $X_i$, $Y_i(0)$, and $Y_i(1)$
around the cutoff $X_i = 0$. Under these conditions, which are made precise
in our Assumption~\ref{A1}, $\tau$ is equal to
\begin{equation*}
  \tau = \lim_{x \to 0+} \mu(x) - \lim_{x \to 0-}(x)
\end{equation*}
where
\begin{equation*}
  \mu(x)= \E(Y_{i} \mid X_{i}=x).
\end{equation*}
For convenience, also define
\begin{equation*}
  \mu^{(\eta)}(x)=\frac{d^{\eta}\mu(x)}{dx^{\eta}}
\end{equation*}
and let
\begin{align*}
  \mu_{+}(x)
  &= \E( Y_{i}(1) \mid X_{i}=x )
  &\mu_{-}(x)
  &= \E( Y_{i}(0) \mid X_{i}=x ) \\
  \sigma^{2}_{+}(x) &= \V( Y_{i}(1) \mid X_{i}=x )
  &\sigma^{2}_{-}(x)&=\V( Y_{i}(0) \mid X_{i}=x ) \\
\intertext{and}
  \mu^{(\eta)}_{+}
  &= \lim_{x \rightarrow 0^{+}}\mu^{(\eta)}(x),
  &\mu^{(\eta)}_{-}
  &= \lim_{x \rightarrow 0^{-}}\mu^{(\eta)}(x),
\end{align*}
where the symbol $\V(\cdot)$ represents the variance.  The effect $\tau$ is
nonparametrically identified because both $\mu_-$ and $\mu_+$ can be estimated
consistently under Assumption~\ref{A1}, which lists standard conditions in the
RD literature. (See, in particular, \citealp{HTV2001}, \citealp{Porter03}, and
CCT.)

@@

Since the conditions for identification only need to hold in a neighborhood
around the cutoff, $\mu_+$ and $\mu_-$ can be estimated by extrapolating from a
local polynomial regression.  We will focus here on local linear
regression.\footnote{%
  See \cite{HTV2001}, \cite{Porter03} or \cite{FanGijbels92} for discussions of
  the properties of local polynomial regressions for boundary problems. The
  bootstrap algorithm proposed in this paper can be extended to accommodate
  higher order polynomials discontinuities in the derivatives of the conditional
  expectation, like ``Kink RD'' design \citep{card2009b}.} %
For this model, if $h$ represents a bandwidth parameter, the estimator of
$\tau$, $\hat\tau(h)$, is defined as
\begin{equation*}
  \hat{\tau}(h) = \hat {\mu}_{+}(h) -\hat{\mu}_{-}(h)
\end{equation*}
with
\begin{align*}
  (\hat {\mu}_{+}(h),\ \hat {\mu}^{(1)}_{+}(h))'
  &= \argmin_{\mu, \beta} \sum_{i=1}^{n}
  \1\{h > X_{i} \geq 0\} (Y_{i} - \mu - X_{i} \beta)^{2}
\intertext{and}
  (\hat {\mu}_{-}(h),\hat {\mu}^{(1)}_{-}(h))'
  &= \argmin_{\mu,\beta} \sum_{i=1}^{n}
  \1\{0 > X_{i} > -h \} (Y_{i} - \mu - X_{i} \beta)^{2}.
\end{align*}
Conventional (naive) confidence intervals can be calculated by using an
asymptotic approximation for $\hat\tau(h)$. In particular, if
\begin{gather}
  \label{eq:1}
  \frac{\hat{\tau}(h)-\tau}{\sqrt{V(h)}} \to^d N(0,1),
  \intertext{with}
  \notag
  V(h) \big/ \V(\hat\tau(h) \mid X_{1},\dots,X_{n}) \to^p 1
\end{gather}
then valid confidence intervals can be constructed through the usual method of
inverting the $t$-test. This procedure gives the widely-used interval estimator
\begin{equation*}
  \hat{\tau}(h) \pm q_{1-\alpha/2} V(h)^{1/2}
\end{equation*}
where $q_{1 - \alpha/2}$ is the $1 - \alpha/2$ quantile of the standard normal
distribution.

The statistical properties of these estimators, however, clearly depend on the
bandwidth parameter $h$, and bandwidths that have desirable properties for point
estimation may not have desirable properties for hypothesis testing or interval
estimation. In particular, for~\eqref{eq:1} to hold, $h$ must satisfy
$n h \to \infty$ and $n h^5 \to 0$. (\citealp{HTV2001}; \citealp{Porter03})
Otherwise, the finite-sample bias of $\hat\tau(h)$ does not converge in
probability to zero quickly enough and it contributes non-negligibly to the
asymptotic distribution in~\eqref{eq:1}. This result holds even though
$\hat\tau(h)$ can be consistent under those conditions.  These bandwidth issues
are relevant in practice because many widely-used bandwidth selection
procedures, most notably the AMSE-optimal bandwidth and cross-validation
bandwidth \citep{IK} do not produce $o_{p}(n^{-1/5})$ bandwidths.

CCT solve this problem by deriving the analytical form of the first-order bias
and explicitly recentering $\hat\tau(h)$. Under weaker assumptions on the
asymptotic behavior of the bandwidth, which we will specify in
Assumption~\ref{A2}, CCT show that the approximate bias of $\hat\tau(h)$ has the
form
\begin{equation*}
  \E(\hat{\tau}(h) \mid X_1,\dots,X_n) - \tau =
  h^{2}\Big[ \tfrac{\mu_{+}^{(2)}}{2}\Bf_{+}(h)
  - \tfrac{\mu_{-}^{(2)}}{2}\Bf_{-}(h) \Big]
  (1+o_{p}(1))
\end{equation*}
where $\Bf_{+}(h)$ and $\Bf_{-}(h)$ are observed quantities that depend on the
kernel, bandwidth, and running variables $X_1,\dots,X_n$; formal definitions of
these terms are given in the Mathematical Appendix as Equations~\eqref{eq:5}
and~\eqref{eq:6}.\footnote{%
  One subtle but important feature of $\Bf_{-}$ and $\Bf_{+}$ is that they only
  depend on the running variables, not the outcomes $Y_1,\dots,Y_n$.} %
The plug-in bias-corrected estimator then requires estimates
for the second derivatives of the conditional mean from above and below the
cutoff, $\mu_{+}^{(2)}$ and $\mu_{-}^{(2)}$, and CCT show that these derivatives
can be estimated by fitting a second order local polynomial, i.e. one order
higher than the polynomial used to obtain $\hat{\tau}$, using a (potentially)
different pilot bandwidth $b$. Their procedure gives the bias-corrected
estimator
\begin{gather*}
  \hat{\tau}'(h, b) = \hat{\tau}(h) - h^{2}
  \Big[\tfrac{\hat{\mu}_{+}^{(2)}(b)}{2} \Bf_{+}(h)
  - \tfrac{\hat{\mu}_{-}^{(2)}(b)}{2}\Bf_{-}(h) \Big]
\end{gather*}
The variance introduced by the bias-correction term does not vanish, so the
naive confidence interval needs not only to be re-centered to correct the bias,
but also rescaled to allow for the additional variability introduced by the bias
correction, resulting in the following asymptotic approximation:
\begin{equation*}
  \frac{\hat{\tau}'(h, b) - \tau}{V'(h, b)^{1/2}} \to^d N(0,1)
\end{equation*}
with $V'(h, b) = V(h) + C(h, b)$ and $C(h, b)$ an additional variance component
generated by the bias-correction term. This new approximation can be used
instead of~\eqref{eq:1} to construct ``bandwidth robust'' confidence intervals,
and CCT provide simulation evidence that their intervals perform well in finite
samples even when the naive interval performs badly.
